### 2024-02-25 presentation/parts/introduction.tex
WIP

\begin{frame}
    \frametitle{Healthcare}
    \begin{quotation}
        \noindent\centering
        Healthcare is the improvement of health via the {\color{dtured}prevention}, {\color{dtured}diagnosis}, {\color{dtured}treatment}, {\color{dtured}amelioration} or {\color{dtured}cure} of {\color{theme-green}disease}, {\color{theme-green}illness}, {\color{theme-green}injury}, and {\color{theme-green}other physical and mental impairments} in people.
    \end{quotation}
\end{frame}

@@

\begin{frame}
    \frametitle{Errors in medical dialogue}
    \begin{itemize}
        \item<1,2>Communication is everywhere in healthcare. 
        \item <1,2>It is complex, involving multiple participants, different contexts, and different purposes.
        \item <2> {\color{dtured} } Failure of communication is a leading cause of medical error contributing to two out of three adverse events \cite{starmer_changes_2014}.
        \item <2> A considerable fraction of all hospital admissions had preventable adverse outcomes (9\% to 16.6\% in AU, NZ, UK, DK) \cite{carver_medical_2024}.
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Documenting medical encounters}
    \begin{itemize}
        \item <1,2> Documentation is a central part of healthcare.
        \item <1,2> E.g. patient records, insurance claims, billing, research, training, legal purposes.
        \vspace{1em}
        \item <2> {\color{dtured}Time}: Physicians spend 34-37\% of their time on documentation \cite{joukes_time_2018, tipping_where_2010, sinsky_allocation_2016}\footnote{Ambulatory care across four specialties in four states and tertiary care at an academic medical center.}.
        \item <2> {\color{dtured}Quality}: Discharge summaries rarely meet all timeline, transmission, and content criteria. \cite{horwitz_comprehensive_2013}\footnote{Outpatient visits, Yale-New Haven Hospital.}
    \end{itemize}

@@

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{itemize}
        \item <1> {\color{dtured}Assist} with documentation.
        \item <1> {\color{dtured}Augment} communication.
        \item <1> {\color{dtured}Improve} decision-making.
        \vspace{1em}
        \item <1> {\color{dtured}Reduce} errors.
        \item <1> {\color{dtured}Save} time.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning}
    \begin{itemize}
        \item <1> {\color{dtured}Data}: Privacy, quality, quantity, diversity.
        \item <1> {\color{dtured}Interpretability}: Trust, ethics, regulation.
        \item <1> {\color{dtured}Explainability}: Transparency, accountability.
        \item <1> {\color{dtured}Robustness}: Adversarial attacks, distribution shift.
        \item <1> {\color{dtured}Bias}: Fairness, transparency.
        \item <1> {\color{dtured}Complexity}: Context, domain, language, culture.
    \end{itemize}

\end{frame}

>>>>

\begin{frame}
    % Background on Corti and the problem of medical communication, diagnosis, and documentation.
    \frametitle{Background}
    \begin{columns}
        \begin{column}{0.6\textwidth}
            FILL ME OUT. \\
            Background on Corti, motivation for project.
        \end{column}
        \begin{column}{0.4\textwidth}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Healthcare}
    \begin{quotation}
        \noindent\centering
        Healthcare is the improvement of health via the \highlight{prevention}, \highlight{diagnosis}, \highlight{treatment}, \highlight{amelioration} or \highlight{cure} of {\color{theme-green}disease}, {\color{theme-green}illness}, {\color{theme-green}injury}, and {\color{theme-green}other physical and mental impairments} in people.
    \end{quotation}
\end{frame}

@@

\begin{frame}
    \frametitle{Errors in medical dialogue}
    \begin{itemize}
        \item<1,2>Communication is everywhere in healthcare. 
        \item <1,2>It is complex, involving multiple participants, different contexts, and different purposes.
        \vspace{1em}
        \item <2> \highlight{Adverse events}: Failure of communication is a leading cause of medical error contributing to two out of three adverse events \cite{starmer_changes_2014}.
        \item <2> \highlight{Preventability}: A considerable fraction of all hospital admissions had preventable adverse outcomes (9\% to 16.6\% in AU, NZ, UK, DK) \cite{carver_medical_2024}.
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Documenting medical encounters}
    \begin{itemize}
        \item <1,2> Documentation is a central part of healthcare.
        \item <1,2> E.g. patient records, insurance claims, billing, research, training, legal purposes.
        \vspace{1em}
        \item <2> \highlight{Time-consuming}: Physicians spend 34-37\% of their time on documentation \cite{joukes_time_2018, tipping_where_2010, sinsky_allocation_2016}\footnote{Ambulatory care across four specialties in four states and tertiary care at an academic medical center.}.
        \item <2> \highlight{Varying quality}: Discharge summaries rarely meet all timeline, transmission, and content criteria. \cite{horwitz_comprehensive_2013}\footnote{Outpatient visits, Yale-New Haven Hospital.}
    \end{itemize}

@@

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{itemize}
        \item <1-> \highlight{Assist} with documentation.
        \item <1-> \highlight{Augment} communication.
        \item <1-> \highlight{Improve} decision-making.
        \vspace{1em}
        \item <2-> \highlight{Reduce} number of impact of medical errors and adverse events.
        \item <2-> \highlight{Free up} time spent on documentation for patient care.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning systems}
    \begin{itemize}
        \item <1-> \highlight{Data}: Quality, quantity, diversity, bias, privacy, ethics.
        \item <2-> \highlight{Task}: Context, domain, language, culture, purpose.
        \vspace{1em}
        \item <3-> \highlight{Interpretability} of how a model works (transparency, accountability, regulation).
        \item <4-> \highlight{Explainability} of model predictions (trust, understanding, feedback).
        \item <5-> \highlight{Fairness} in treatment of different groups of people.
        \item <6-> \highlight{Robustness} to noise, outliers, adversarial attacks, and distribution shift.
    \end{itemize}
\end{frame}

### 2024-02-25 presentation/parts/overview_brief.tex
WIP

                    \tikzmarkin<1->{hierarchical-8}(0.1,-0.3)(-0.1,0.4)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 4}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{hierarchical vaes know what they don't know}} & \tikzmarkend{hierarchical-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{modelagnostic-8}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 5}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{model-agnostic out-of-distribution detection\\ using combined statistical tests}} & \tikzmarkend{modelagnostic-8} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{brief-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<-1>{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<-1>{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{benchmarking-8}(0.1,-0.3)(-0.1,0.4)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 7}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{benchmarking latent variable models for speech}} & \tikzmarkend{benchmarking-8} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    % \tikzmarkin<1->{automated-8}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 8}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{automated medical coding on mimic-iii and \\mimic-iv: a critical review and replicability study}} & \tikzmarkend{automated-8} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{retrospective-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-8} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

>>>>

                    \tikzmarkin<1->{hierarchical-7}(0.1,-0.3)(-0.1,0.4)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 4}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{hierarchical vaes know what they don't know}} & \tikzmarkend{hierarchical-7} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{modelagnostic-7}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 5}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{model-agnostic out-of-distribution detection\\ using combined statistical tests}} & \tikzmarkend{modelagnostic-7} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{brief-7}(0.1,-0.4)(-0.1,0.6)
                    & {\color<-1>{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<-1>{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-7} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{benchmarking-7}(0.1,-0.3)(-0.1,0.4)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 7}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{benchmarking latent variable models for speech}} & \tikzmarkend{benchmarking-7} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    % \tikzmarkin<1->{automated-7}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 8}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{automated medical coding on mimic-iii and \\mimic-iv: a critical review and replicability study}} & \tikzmarkend{automated-7} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{retrospective-7}(0.1,-0.4)(-0.1,0.6)
                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-7} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

### 2024-02-25 presentation/parts/overview_discussion.tex
WIP

                    \tikzmarkin<1->{hierarchical-8}(0.1,-0.3)(-0.1,0.4)
                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 4}}}         & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{hierarchical vaes know what they don't know}} & \tikzmarkend{hierarchical-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{modelagnostic-8}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 5}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{model-agnostic out-of-distribution detection\\ using combined statistical tests}} & \tikzmarkend{modelagnostic-8} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{brief-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<1->{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{benchmarking-8}(0.1,-0.3)(-0.1,0.4)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 7}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{benchmarking latent variable models for speech}} & \tikzmarkend{benchmarking-8} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    % \tikzmarkin<1->{automated-8}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 8}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{automated medical coding on mimic-iii and \\mimic-iv: a critical review and replicability study}} & \tikzmarkend{automated-8} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{retrospective-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-8} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

>>>>

                    \tikzmarkin<1->{hierarchical-6}(0.1,-0.3)(-0.1,0.4)
                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 4}}}         & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{hierarchical vaes know what they don't know}} & \tikzmarkend{hierarchical-6} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{modelagnostic-6}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 5}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{model-agnostic out-of-distribution detection\\ using combined statistical tests}} & \tikzmarkend{modelagnostic-6} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{brief-6}(0.1,-0.4)(-0.1,0.6)
                    & {\color<1->{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-6} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    % \tikzmarkin<1->{benchmarking-6}(0.1,-0.3)(-0.1,0.4)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 7}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{benchmarking latent variable models for speech}} & \tikzmarkend{benchmarking-6} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    % \tikzmarkin<1->{automated-6}(0.1,-0.4)(-0.1,0.6)
                    % & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 8}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{automated medical coding on mimic-iii and \\mimic-iv: a critical review and replicability study}} & \tikzmarkend{automated-6} \\
                    % \addlinespace[0.5em]
                    % \addlinespace[0.5em]

                    \tikzmarkin<1->{retrospective-6}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-6} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

### 2024-02-25 presentation/parts/overview_presentation.tex
WIP

\newcommand{\tikzautomated}{%
    \resizebox{!}{0.8\textheight}{%
        \begin{tikzpicture}[x=1cm,y=1cm]
            \node [nearly transparent, mybox, fill=presentation_orange] at (0,5) (predictions) {};
            \foreach \i in {-11,...,11} {
                \fill[nearly transparent, myrect, fill=presentation_orange_shaded] (0.2*\i,4.8) rectangle ++(0.1,0.4);
            }
            \node [nearly transparent] at (0,5) {\small\textsc{predictions}};

@@

                    \tikzmarkin<1->{modelagnostic-2}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 5}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{model-agnostic out-of-distribution detection\\ using combined statistical tests}} & \tikzmarkend{modelagnostic-2} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{benchmarking-2}(0.1,-0.3)(-0.1,0.4)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 7}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{benchmarking latent variable models for speech}} & \tikzmarkend{benchmarking-2} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    \tikzmarkin<1->{automated-2}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 8}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{automated medical coding on mimic-iii and \\mimic-iv: a critical review and replicability study}} & \tikzmarkend{automated-2} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1>\tikzoverview
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

>>>>

\newcommand{\tikzautomated}{%
    \resizebox{!}{0.8\textheight}{%
        \begin{tikzpicture}[x=1cm,y=1cm]
            \node [mybox, fill=presentation_orange] at (0,5) (predictions) {};
            \foreach \i in {-11,...,11} {
                \fill[myrect, fill=presentation_orange_shaded] (0.2*\i,4.8) rectangle ++(0.1,0.4);
            }
            \node [] at (0,5) {\small\textsc{predictions}};

@@

                    \tikzmarkin<1->{modelagnostic-2}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{dtured!40}\makecell[l]{\textsc{\itshape chapter 5}\\\\}}     & {\color<2->{dtured!40} \bfseries \scshape \Large \makecell[l]{model-agnostic out-of-distribution detection\\ using combined statistical tests}} & \tikzmarkend{modelagnostic-2} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{benchmarking-2}(0.1,-0.3)(-0.1,0.4)
                    & {\color<2->{dtured!40}\makecell[l]{\textsc{\itshape chapter 7}}}         & {\color<2->{dtured!40} \bfseries \scshape \Large \makecell[l]{benchmarking latent variable models for speech}} & \tikzmarkend{benchmarking-2} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

                    \tikzmarkin<1->{automated-2}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{dtured!40}\makecell[l]{\textsc{\itshape chapter 8}\\\\}}     & {\color<2->{dtured!40} \bfseries \scshape \Large \makecell[l]{automated medical coding on mimic-iii and \\mimic-iv: a critical review and replicability study}} & \tikzmarkend{automated-2} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1->\tikzoverview
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}
